```{r}
# load packages
# Load packages
library(LaplacesDemon)
library(sjPlot)
library(tidyverse)
library(broom)
library(lme4)
library(ggExtra)
library(ggthemes)
library(scales)
library(Hmisc)
library(Metrics)
library(plotrix)
library(pheatmap) # this package lets you make nice heatmaps
library(RColorBrewer) # import color palettes
library(networkD3) # This package lets you make and plot Sankey diagrams
library(zoo) # some mathematical functions that are useful
library(tibbletime)
library(agricolae) # post hoc Tukey test
library(ggallin) # this is for the pseudolog10_trans function used in coeff plots in Figure2_Analysis
library(car)
library(arrow)
library(cowplot)
# library(glmmTMB)
library(furrr)
library(DHARMa)
library(effects)
library(haven) #for reading sav data
library(jtools) #for transformaing model summaries
library(ROCR) #for calculating area under the curve (AUC) statistics
future::plan(multisession)

```

# subset the data acccording to trial type
```{r}
spatial_firing <- readRDS(file="all_cells_for_R_longform.Rda")

spatial_firing$rolling_classifier <- replace(spatial_firing$rolling_classifier, spatial_firing$rolling_classifier == "", NA)
spatial_firing$rolling_classifier <- replace(spatial_firing$rolling_classifier, spatial_firing$rolling_classifier == "nan", NA)
spatial_firing$rolling_classifier <- replace(spatial_firing$rolling_classifier, spatial_firing$rolling_classifier == "N", NA)
spatial_firing <- na.omit(spatial_firing)

beaconed_data <- spatial_firing[spatial_firing$trial_type == 0,]
non_beaconed_data <- spatial_firing[spatial_firing$trial_type == 1,]
probe_data <- spatial_firing[spatial_firing$trial_type == 2,]
```

# set up the formulas for p coding
```{r}
formula_full <- formula(p_coding ~ behavioural_outcome + (1 | mouse_id / session_id / cluster_id) + (0 + behavioural_outcome | mouse_id / session_id / cluster_id))
formula_null <- formula(p_coding ~ (1 | mouse_id / session_id / cluster_id) + (0 + behavioural_outcome | mouse_id / session_id / cluster_id))

```


# run glmer for beacoend trials
```{r}
beaconed_model_full <- lme4::glmer(formula = formula_full, 
                      data = beaconed_data,
                      na.action = na.exclude,
                      family = binomial(link = "logit"),
                      control=lme4::glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

beaconed_model_null <- lme4::glmer(formula =formula_null, 
                      data = beaconed_data,
                      na.action = na.exclude,
                      family = binomial(link = "logit"),
                      control=lme4::glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
```

compare the full model with the null model
```{r}
anova(beaconed_model_full,beaconed_model_null)
```
# run glmer for nonbeacoend trials
```{r}
non_beaconed_model_full <- lme4::glmer(formula = formula_full, 
                      data = non_beaconed_data,
                      na.action = na.exclude,
                      family = binomial(link = "logit"),
                      control=lme4::glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

non_beaconed_model_null <- lme4::glmer(formula = formula_null, 
                      data = non_beaconed_data,
                      na.action = na.exclude,
                      family = binomial(link = "logit"),
                      control=lme4::glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
```
compare the full model with the null model
```{r}
anova(non_beaconed_model_full,non_beaconed_model_null)
```

# run glmer for probe trials
```{r}
probe_model_full <- lme4::glmer(formula = formula_full, 
                      data = probe_data,
                      na.action = na.exclude,
                      family = binomial(link = "logit"),
                      control=lme4::glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

probe_model_null <- lme4::glmer(formula = formula_null, 
                      data = probe_data,
                      na.action = na.exclude,
                      family = binomial(link = "logit"),
                      control=lme4::glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
```

compare the full model with the null model
```{r}
anova(probe_model_full,probe_model_null)
```

# set up the formulas for d coding
```{r}
formula_full <- formula(d_coding ~ behavioural_outcome + (1 | mouse_id / session_id / cluster_id) + (0 + behavioural_outcome | mouse_id / session_id / cluster_id))
formula_null <- formula(d_coding ~ (1 | mouse_id / session_id / cluster_id) + (0 + behavioural_outcome | mouse_id / session_id / cluster_id))

```


# run glmer for beacoend trials
```{r}
beaconed_model_full <- lme4::glmer(formula = formula_full, 
                      data = beaconed_data,
                      na.action = na.exclude,
                      family = binomial(link = "logit"),
                      control=lme4::glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

beaconed_model_null <- lme4::glmer(formula =formula_null, 
                      data = beaconed_data,
                      na.action = na.exclude,
                      family = binomial(link = "logit"),
                      control=lme4::glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
```

compare the full model with the null model
```{r}
anova(beaconed_model_full,beaconed_model_null)
```
# run glmer for nonbeacoend trials
```{r}
non_beaconed_model_full <- lme4::glmer(formula = formula_full, 
                      data = non_beaconed_data,
                      na.action = na.exclude,
                      family = binomial(link = "logit"),
                      control=lme4::glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

non_beaconed_model_null <- lme4::glmer(formula = formula_null, 
                      data = non_beaconed_data,
                      na.action = na.exclude,
                      family = binomial(link = "logit"),
                      control=lme4::glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
```
compare the full model with the null model
```{r}
anova(non_beaconed_model_full,non_beaconed_model_null)
```

# run glmer for probe trials
```{r}
probe_model_full <- lme4::glmer(formula = formula_full, 
                      data = probe_data,
                      na.action = na.exclude,
                      family = binomial(link = "logit"),
                      control=lme4::glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

probe_model_null <- lme4::glmer(formula = formula_null, 
                      data = probe_data,
                      na.action = na.exclude,
                      family = binomial(link = "logit"),
                      control=lme4::glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
```

compare the full model with the null model
```{r}
anova(probe_model_full,probe_model_null)
```
