---
title: "ConvertPickletoRda"
author: "Harry Clark"
date: "04/04/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### ----------------------------------------------------------------------------------------------- ###

## This code loads dataframes with spatial firing of neurons in the virtual reality

Aim: We want to load dataframes from python output which are in pickled format, and save them in Rs dataframe format (.Rda). 

### ----------------------------------------------------------------------------------------------- ###


First we need to set up the python environment. This is so we can call a python script from R that loads the pickled dataframes and sends it back to the R workspace. 
The python environment needs to be >v.3 as 2.7 (system python) doesn't have Pandas package which is needed to open dataframes

To find the path in Linux use 'type -a python3' in the terminal.
```{r}
require(reticulate) # package that allows R to call python code
Sys.setenv(RETICULATE_PYTHON = "C:\\Users\\harry\\anaconda3\\envs\\py38\\python.exe")
```


### ----------------------------------------------------------------------------------------------- ###

### LOAD ALL MICE ALL DAYS DATAFRAMES

### ----------------------------------------------------------------------------------------------- ###

## Loading dataframe for all mice and days (all curated cells from one animal/multiple animals)

1. load python code to load pickle dataframe
```{r}
source_python("picklereader.py") # run python script which loads the dataframes - should be in working directory
```

2. Load all cohorts, and necessary columns for analysis

```{r}
dataframe_to_load <- "data_in/all_cells_for_R_longform.pkl"
all_cells_for_R_longform <- read_pickle_file(file.path(dataframe_to_load)) 
```
### ----------------------------------------------------------------------------------------------- ###

### Save concatenated frames for future loading

### ----------------------------------------------------------------------------------------------- ###
6. Save final concatenated dataframe
```{r}
saveRDS(all_cells_for_R_longform, file="all_cells_for_R_longform.Rda")
```